Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2022-03-10 doc/peakcharacterization_manuscript.Rmd
fixing the manuscript

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      dpi = 600, 
                      dev = "png", 
                      dev.args = list(type = "cairo"),
                      fig.process = dn_figure_rename)
```

>>>>

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      dpi = 600, 
                      dev = "png", 
                      dev.args = list(type = "cairo"),
                      fig.process = dn_modify_path)
```
